---
title: "Distribución de Grupos Dx de la Base UIID"
output:
  html_document:
    df_print: paged
  html_notebook:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

## Llamando librerías
```{r}
library(ggplot2)
library(dplyr)
# library(plotly)
```

## Leemos datos
```{r}
base<-read.csv("../data/UIID_20190201.csv",header=T)
# class(base)
base01<-base%>%
  as_data_frame()%>%
  select(gruposos,grupodx)%>%
  filter(grupodx!=0)
# class(base01)
base01
```

## Distribución por grupo diagóstico

```{r}
gb01<-base01%>%
  group_by(gruposos)%>%
  summarise(n_px=n(),
            per_px=round(n_px/nrow(.),4),
            porcentaje= paste0(formatC(100 * per_px, digits = 2, format = "f"), "%"))%>%
  rename(Grupo=gruposos)
gb01
```
```{r}
## Create a basic bar
pie00 <- ggplot(gb01, aes(x="", y=n_px, fill=Grupo)) + geom_bar(stat="identity", width=1)+
  coord_polar("y", start=0) + geom_text(aes(label = n_px), position = position_stack(vjust = 0.5),size=2) +
  scale_fill_manual(values=c("#55DDE0", "#33658A", "#2F4858", "#F6AE2D", "#F26419", "#999999","#CC6666", "#9999CC", "#66CC99")) +
  labs(x = NULL, y = NULL, fill = NULL, title = "Grupos Diagnósticos (n)")+
  theme_classic() + theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5, color = "#666666"))
pie00
```

```{r}
## Create a basic bar
pie01<- ggplot(gb01, aes(x="", y=per_px, fill=Grupo)) + geom_bar(stat="identity", width=1) +
  ## Convert to pie (polar coordinates) and add labels
  coord_polar("y", start=0) + geom_text(aes(label = paste0(round(per_px*100,4), "%")), position = position_stack(vjust =0.5),size=2) + 
  ## Add color scale (hex colors)
  scale_fill_manual(values=c("#55DDE0", "#33658A", "#2F4858", "#F6AE2D", "#F26419", "#999999","#CC6666", "#9999CC", "#66CC99"))  + 
  # Remove labels and add title
  labs(x = NULL, y = NULL, fill = NULL, title = "Grupos Diagnósticos (%)") + theme_classic() + theme(axis.line = element_blank(), ## Tidy up the theme
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5, color = "#666666"))
pie01
```


```{r}
## Create pichart with pie() function
color<-c("#55DDE0", "#33658A", "#2F4858", "#F6AE2D", "#F26419", "#999999","#CC6666", "#9999CC", "#66CC99")
#,col=c("#55DDE0", "#33658A", "#2F4858", "#F6AE2D", "#F26419", "#999999","#CC6666", "#9999CC", "#66CC99"))
# c("yellow2","olivedrab3","orangered3","lightblue","red","orange","pink","black","darkblue")
pie(gb01$per_px,labels=gb01$porcentaje,clockwise=T,main="Grupos Diagnósticos (%)",col=color)
legend("topleft",legend=as.character(gb01$Grupo),cex=0.35,fill=color)